Honey Bee Colonies Impacted by Varroa, American Foulbrood and Global Warming

### 2024-08-01 starter-analysis-exercise/products/report/manuscript_final-2.qmd
additional updates

[@epa_climate_indicator] ***Global warming trends from 1900-2024***

@@

![](/images/dead-bees-hive-colony-collapse-600nw-2289939105.webp)

#Citation section To cite other work (important everywhere, but likely
happens first in introduction), make sure your references are in the
bibtex file specified in the YAML header above and have the right bibtex
key. Then you can include like this:

Examples of reproducible research projects can for instance be found in
[@mckay2020; @mckay2020a].

#Here are the BibTex entries for citations:

Using this in RMarkdown: #Make sure to save these entries in a file
names'reference.bib' and include it in your R Markdown document like
this:

>>>>

[@epa_climate] ***Global warming trends from 1900-2024***

@@

![](/images/dead-bees-hive-colony-collapse-600nw-2289939105.webp)
{{< pagebreak >}}
